\begin{enumerate}


\item This study is only valid for the purpose and use specified in sections H and I of this report and when it is signed by the valuator.
\item The statements of facts, data, and documents provided by the requester for the preparation of this report are assumed to be true and correct.
\item  The analysis and opinions reported in this report are limited only by the assumptions and limiting conditions reported and are the result of the professional and impartial conclusions of the signing valuator.
\item  The signing valuator has no present or future interest in the conclusive figures that are the subject of this report, nor does the valuator have personal interests or bias with respect to the involved parties.
\item  The economic compensation of the valuator is not conditioned on the report of a predetermined or directed value that favors the requester's cause.
\item  This valuation report may only be used in its entirety and not in parts. No part of the report may be used in conjunction with any unrelated study. The publication of the report or any of its parts without the written authorization of the undersigned Public Broker is prohibited. This appraisal may not be used by any person or entity other than the one to which it is addressed or for a purpose or use other than stipulated.
\item  This study does not validate or indicate the legal, accounting, and/or tax treatment of the conclusive figures in the report in accordance with the financial information standards (NIF), the Income Tax Law, the VAT Law, and other applicable regulations.
	
\end{enumerate}