




\begin{enumerate}[\indent a)]

\item It is assumed that this appraisal is in response to a request for professional services based on good faith between the parties involved, namely the applicant and the Appraiser. Therefore, the verbal and written information provided, if any, is understood to be correct as of the date of this appraisal. Additionally, the applicant has stated that they do not have additional information that could affect the values expressed in this report.

\item After thoroughly reviewing this appraisal, the applicant declares that they do not anticipate any underlying, hidden, or extraordinary circumstances that have not been properly reported to the undersigned.

\item  The existence of potential liens on the valued assets (stock certificates) was not verified. For the determination of this fair value, no liens on the equity capital subject to valuation are considered.

\item This document is limited to an estimation of the fair value of the Equity Capital based on the valuation models presented in its respective chapter, except for errors or omissions. This is based on variations in the models themselves and the economic environment, and consequently, as a limitation, the assumptions of fundamental reasons for projection and calculations based on the information received.


\item This report is issued exclusively for the date contained in this report, with a valuation date of \textcolor{principal}{\fechaInforme}. Changes in external or internal factors of the company under analysis in its financial figures may occur after that date, which could affect the conclusive value contained in this report.

\item For the practice of this appraisal, only the figures provided by the applicant and the documents referred to in paragraph \autoref{sec:nn} of this report were valued and studied. Likewise, the applicant, through its legal representative, stated that they do not have additional information that could serve as a basis for modifying the figures indicated here. In the same vein, there has been no independent review of the content and accuracy of this documentation, and the analysis and results could be affected if this information is not correct and/or precise.

\item The information received by the appraiser for analysis corresponds to relevant information from the company whose Equity capital was subject to valuation, so the confidentiality of the information is assumed, and its use is limited to this report.

\item All criteria used for valuation exclude any speculative or particular considerations at a given moment. The ownership of the intangible asset and the company is assumed according to the currently known situation. Likewise, the current market behaviors are assumed as constant (\textit{ceteris paribus}).

\item The projections made for the value estimation referred to in this document are not predictions of the future; they are the appraiser's best estimate of the current conditions projected into the future regarding the financial figures of the company. The appraiser cannot guarantee that these forecasts and estimates will materialize.

\item The analyses, opinions, and conclusions reported are limited by the assumptions and limiting conditions indicated and are my own professional and impartial analyses, opinions, and conclusions.

\item The statements made by the applicant of this valuation report are taken as true. The undersigned assumes no responsibility for the accuracy and correctness of such statements and information provided by the applicant.

\item The conclusive value of this valuation report should not necessarily be considered as the price or consideration to be set for the sale, purchase, transfer, registration, assignment, or transmission of the asset subject to the valuation contained in this document.

\item This valuation report should not necessarily be considered as a recommendation for the sale, purchase, transfer, assignment, transmission, or establishment of a guarantee for the assets covered by it, nor for carrying out any type of business, investment, or operation with it.

\item This valuation report was prepared for \textcolor{principal}{\empresaSolicitante} and its use is limited to the purpose specified therein. Accordingly, the appraiser assumes no responsibility towards third parties for the content of this valuation report. The appraiser does not provide any warranty to third parties (including investors) regarding the content of this valuation report.

\item This valuation report may only be used in its entirety and not in parts. No part of the report may be used in conjunction with any study other than this one. The publication of this valuation report or any of its parts without the written authorization of the appraiser is prohibited. Additionally, this valuation report may not be used by any entity other than the one to which it is addressed or for a purpose or use other than stipulated.

\end{enumerate}









