\textcolor{principal}{DEFINITIONS AND CONCEPTS.}

\begin{enumerate}[\indent\itshape a)]

\item \textcolor{principal}{\textit{EQUITY}}
\textit{It is the difference between a company's assets and liabilities and consists of the sum of all equity accounts, including share capital, reserves, accumulated profits, and current-year profits.}

\item  \textcolor{principal}{\textit{INVESTED CAPITAL}}
\textit{These are the assets that make up a company's Tangible Assets. Invested Capital typically reflects the investment made by investors to start a company and additional capital contributions made during its operation. Its calculation usually corresponds to Total Assets minus Current Liabilities, or alternatively, Non-Current Assets plus Working Capital.}

\item \textcolor{principal}{\textit{REPORT DATE}}
\textit{It corresponds to the date on which the valuation document was prepared and signed. It may be the same as or different from the valuation date.}

\item \textcolor{principal}{\textit{VALUATION DATE}}
\textit{It is the date that the appraiser will record at the moment of closing values in their valuation work. It may be the same as or different from the report date.}

\item \textcolor{principal}{\textit{PURPOSE OF THE VALUATION}}
\textit{It is the explicit intention to determine a type of value that will be estimated based on the assets to be appraised, the valuation specialty, and the use of the appraisal specified by the requester.}

\item \textcolor{principal}{\textit{USE OF THE APPRAISAL}}
\textit{It is the intended purpose of the report, as explicitly stated by the service requester.}

\item \textcolor{principal}{\textit{BOOK VALUE}}
\textit{It is the amount at which an accounting entry is recorded in the accounting books, whether it represents the initial cost, the updated cost, the estimated cost, or the appraised value. It represents the value at which any property, right, asset, debt, or obligation is recorded in the accounting books. Book value represents only ``book figures'' and may be different from the market value, fair value, real value, replacement value, liquidation value, etc.}

%\item \textcolor{principal}{\textit{ORDERLY SALE VALUE}}
\textit{It is the estimated price that could be obtained from a sale in the open market, in a period of time just sufficient to find a buyer or buyers, where the seller has an urgency to sell, and both parties act with knowledge and under the premise that the assets are sold in the condition and location in which they are.}

%\item \textcolor{principal}{\textit{FORCED LIQUIDATION VALUE}}
\textit{It is the gross amount, expressed in monetary terms, that is expected to be obtained from a properly advertised sale carried out in the open market, in which the seller is obliged to sell immediately by court order "as is, where is" the asset. In some cases, it may involve a reluctant seller and a buyer or buyers who purchase with knowledge of the disadvantage for the seller.}

\item \textcolor{principal}{\textit{FAIR VALUE}}
\textit{According to its definition as inserted in the publication of IFRS (International Financial Reporting Standards) by the International Accounting Standards Committee Foundation and by the Mexican Institute of Public Accountants (IMCP), it states, ``...The amount for which an asset could be exchanged or a liability settled between knowledgeable and willing parties in an arm's length transaction...''}

\end{enumerate}




